---
title: "Lego,Worksheet#4"
output:
  pdf_document: default
  html_document: default
date: "2023-10-25"
---
##1. The table below shows the data about shoe size and height. Create a data frame.
##a. Describe the data.
```{r}
library(readr)
Shoe_Data <- read_csv("Shoe Data.csv")
View(Shoe_Data[,1:2])
```
##b. Create a subset by males and females with their corresponding shoe size and height.
##What its result? Show the R scripts.
```{r}
male<-subset(Shoe_Data, Gender == "M" )
male
female<-subset(Shoe_Data, Gender == "F")
female

```
##c. Find the mean of shoe size and height of the respondents. Write the R scripts and its result.
```{r}
mean(Shoe_Data$`Shoe Size`)
mean(Shoe_Data$`Shoe Height`)
```
##d. Is there a relationship between shoe size and height? Why?
##Yes there is a relationship between shoe size and height because as you can see in the table taller individuals have larger shoe size.The taller the respondents is ther larger their shoe size is.

##2. Construct character vector months to a factor with factor() and assign the result tofactor_months_vector.
##Print out factor_months_vector and assert that R prints out the factor levels below the actual values.
```{r}
months_vector<- c("March","April","January","November","January","September","October","September","November","August","January","November","November","February","May","August","July","December","August","August","September","November","February","April")
factor_months_vector <- factor(months_vector)
factor_months_vector
```
##3. Then check the summary() of the months_vector and factor_months_vector.
```{r}
summary(months_vector)
summary(factor_months_vector)
```
Interpret the results of both vectors. Are they both equally useful in this case?
##The summary of "months_vector" will reflect the original order and frequency of months in data, while the "factor_months_vector" summary will display the months in a sorted order based on the levels of the factor. So, they may not be equally useful, and the choice between them depends on specific analysis needs.

##4. Create a vector and factor for the table below.
```{r}
direction<-c("East","West", "North")
frequency<- c(1,4,3)
direction
frequency
```
```{r}
factor_months_vector <- factor(months_vector)
factor_months_vector
```
```{r}
new_order_data <- factor(direction,levels = c("East","West","North"))
print(new_order_data)
```

##5. Enter the data below in Excel with file name = import_march.csv
```{r}
library(readr)
import_march <- read_csv("import_march.csv")
View(import_march)
```

##6. If else
```{r}
int6<- readline(prompt= "Enter a number 1 to 50")
if(int6>=50){
  print("THe number selected is beyond the range of 1")
}else if (int6==20){
  print (TRUE)
}else {
  int6
}
```
##7At ISATU University’s traditional cafeteria, snacks can only be purchased with bills. A long-standing rule at the concession stand is that snacks must be purchased with as few coins as possible. There are three types of bills: 50 pesos, 100 pesos, 200 pesos, 500 pesos, 1000 pesos.
##a. Write a function that prints the minimum number of bills that must be paid, given the price of the snack.
```{r}
bills<- c(50, 100, 200, 500, 1000)
price<-as.numeric(readline(prompt= "Enter price a price: "))
  if (price == 50){
    cat("Minimum bills is: ")
    cat(bills[c(1)])
  }else if (price <= 150){
    cat("Minimum bills is: ")
    cat(bills [c(1,2)])
  }else if (price <= 450){
    cat("Minimum bills is: ")
    cat(bills [c(1,2,3)])
  }else if (price <= 950){
    cat("Minimum bills is: ")
    cat(bills [c(1,2,3,4)])
  }else if (price >= 1000){
    cat("Minimum bills is: ")
    cat(bills [c(1,2,3,4,5)])
  }
```
##8The following is each student’s math score for one semester. Based on this, answer the following questions.
##a. Create a dataframe from the above table. Write the R codes and its output.
```{r}
name<- c("Annie", "Thea", "Steve", "Hanna")
grade1<- c(85, 65, 75, 95)
grade2<- c(65, 75, 55, 75)
grade3<- c(85, 90, 80, 100)
grade4<- c(100, 90, 85, 90)

math<-data.frame(
  Name = c(name),
  Grade1 = c(grade1),
  Grade2 = c(grade2),
  Grade3 = c(grade3),
  Grade4 = c(grade4)
)
math
```

##b. Without using the rowMean function, output the average score of students whose average math score over 90 points during the semester. write R code and its output.
```{r}
Average <- (math$Grade1 + math$Grade2 + math$Grade3 + math$Grade4) / 4
math$Average<-c(Average)
high_average_students <- math[math$Average >90 ]
i<-c(1:4)
if (math$Average[1]> 90){
  cat(math$Average[1], "'s average grade this semester is", math$Average[1], ".\n")
}else if (math$Average[2]> 90){
  cat(math$Average[2], "'s average grade this semester is", math$Average[2], ".\n")
}else if (math$Average[3]> 90){
  cat(math$Average[3], "'s average grade this semester is", math$Average[3], ".\n")
}else if (math$Average[4]> 90){
  cat(math$Average[4], "'s average grade this semester is", math$Average[4], ".\n")
}
```

##c. Without using the mean function, output as follows for the tests in which the average score was less than 80 out of 4 tests.
```{r}
test<-c("1st", "2nd", "3rd", "4th")
ave1<-sum(math$Grade1)/4
ave2<-sum(math$Grade2)/4
ave3<-sum(math$Grade3)/4
ave4<-sum(math$Grade4)/4

if (ave1<80){
  cat("The",test[1], "test was difficult")
}else if (ave2<80){
  cat("The",test[2], "test was difficult")
}else if (ave3<80){
  cat("The",test[3], "test was difficult")
}else if (ave4<80){
  cat("The",test[4], "test was difficult")
}
```
##d. Without using the max function, output as follows for students whose highest score for a semester exceeds 90 points. Example Output: Annie’s highest grade this semester is 95.

```{r}
for (i in 1:4){
  if(math$Grade1[i]>90){
    cat(math$Name[i], "highest grade this semester is", round (math$Grade1[i],2), ".\n")
}}
```
```{r}
for (i in 1:4){
  if(math$Grade2[i]>90){
    cat(math$Name[i], "highest grade this semester is", round (math$Grade2[i],2), ".\n")
}}
```

```{r}
for (i in 1:4){
  if(math$Grade3[i]>90){
    cat(math$Name[i], "highest grade this semester is", round (math$Grade3[i],2), ".\n")
}}
```
```{r}
for (i in 1:4){
  if(math$Grade4[i]>90){
    cat(math$Name[i], "highest grade this semester is", round (math$Grade4[i],2), ".\n")
}}
```