---
title: "Lego,Worksheet#4"
output: html_document
date: "2023-10-25"
---
#1. The table below shows the data about shoe size and height. Create a data frame.
#a. Describe the data.
```{r}
library(readr)
Shoe_Data <- read_csv("worksheet/Shoe Data.csv")
View(Shoe_Data[,1:2])
```
#b. Create a subset by males and females with their corresponding shoe size and height.
#What its result? Show the R scripts.
```{r}
male<-subset(Shoe_Data, Gender == "M" )
male
female<-subset(Shoe_Data, Gender == "F")
female

```
#c. Find the mean of shoe size and height of the respondents. Write the R scripts and its result.
```{r}
mean(Shoe_Data$`Shoe Size`)
mean(Shoe_Data$`Shoe Height`)
```
##d. Is there a relationship between shoe size and height? Why?
##Yes there is a relationship between shoe size and height because as you can see in the table taller individuals have larger shoe size.The taller the respondents is ther larger their shoe size is.

#2. Construct character vector months to a factor with factor() and assign the result tofactor_months_vector.
#Print out factor_months_vector and assert that R prints out the factor levels below the actual values.
```{r}
months_vector<- c("March","April","January","November","January","September","October","September","November","August","January","November","November","February","May","August","July","December","August","August","September","November","February","April")
factor_months_vector <- factor(months_vector)
factor_months_vector
```
#3. Then check the summary() of the months_vector and factor_months_vector.
```{r}
summary(months_vector)
summary(factor_months_vector)
```
Interpret the results of both vectors. Are they both equally useful in this case?
##The summary of "months_vector" will reflect the original order and frequency of months in data, while the "factor_months_vector" summary will display the months in a sorted order based on the levels of the factor. So, they may not be equally useful, and the choice between them depends on specific analysis needs.

##4. Create a vector and factor for the table below.
```{r}
direction<-c("East","West", "North")
frequency<- c(1,4,3)
direction
frequency
```
```{r}
factor_months_vector <- factor(months_vector)
factor_months_vector
```
```{r}
new_order_data <- factor(direction,levels = c("East","West","North"))
print(new_order_data)
```

#5. Enter the data below in Excel with file name = import_march.csv
