---
title: "RWorksheet_Lego#4c"
author: "Aira Mia Lego BSIT 2B"
date: "2023-11-21"
output: pdf_document
---
## R Markdown 4c
##1. Use the dataset mpg
##a. Show your solutions on how to import a csv file into the environment.
```{r}
library(readr)
mpg <- read_csv("mpg.csv")
mpg
```

##b.Which variables from mpg dataset are categorical?
```{r}

```

##c. Which are continuous variables?
```{r}

```

##2. Which manufacturer has the most models in this data set? Which model has the most variations? Show your answer.

```{r}
mdl<- factor(mpg$model)
summary(mdl)
max(summary(mdl))
man<- factor(mpg$manufacturer)
summary(man)
max(summary(man))
```

##a.Group the manufacturers and find the unique models. Show your codes and result.
```{r}
man2a<- factor(mpg$manufacturer)
summary(man2a)
min(summary(man2a))
```
```{r}
mdl2a<- factor(mpg$manufacturer)
summary(mdl2a)
min(summary(mdl2a))
```

##b.Graph the result by using plot() and ggplot(). Write the codes and its result.
```{r}
ggplot(data_ggp, aes(x = mpg$manufacturer, y = mpg$model)) + geom_bar(stat = "identity") 

data_ggp <- data.frame(mpg$manufacturer,mpg$model)
```

##Same dataset will be used. You are going to show the relationship of the model and the manufacturer.

##a. What does ggplot(mpg, aes(model, manufacturer)) + geom_point() show?
```{r}
 ggplot(mpg, aes(model, manufacturer)) + geom_point()
```
##b. For you, is it useful? If not, how could you modify the data to make it more informative?
```{r}
ggplot(mpg, aes(model, manufacturer)) + geom_point()
```

```{r}

```