---
title: "RWorksheet_Lego#4c"
author: "Aira Mia Lego BSIT 2B"
date: "2023-11-21"
output: pdf_document
---
## R Markdown 4c
##1. Use the dataset mpg
##a. Show your solutions on how to import a csv file into the environment.
```{r}
library(readr)
mpg <- read.csv("mpg.csv")
mpg
```

##b.Which variables from mpg dataset are categorical?
```{r}
num1a<- sapply(mpg, function(x) is.factor(x)|| is.character(x))
cat("Categorical Variables:  ", names(mpg)[num1a], "\n")
```

##c. Which are continuous variables?
```{r}
num1b<- sapply(mpg, function(x) is.numeric(x) && !is.factor(x) && !is.character(x))
cat("Continuous Variables: ", names(mpg)[num1b], "\n")
```

## 2. Which manufacturer has the most models in this data set? Which model has the most variations? Show your answer.

```{r}
mdl<- factor(mpg$model)
summary(mdl)
max(summary(mdl))
man<- factor(mpg$manufacturer)
summary(man)
max(summary(man))
```

##a.Group the manufacturers and find the unique models. Show your codes and result.
```{r}
man2a<- factor(mpg$manufacturer)
summary(man2a)
min(summary(man2a))
```
```{r}
mdl2a<- factor(mpg$manufacturer)
summary(mdl2a)
min(summary(mdl2a))
```

##b.Graph the result by using plot() and ggplot(). Write the codes and its result.
```{r}
library(ggplot2)
ggplot(mpg, aes(x = manufacturer, y = model,color= class)) + geom_point() 
```

## Same dataset will be used. You are going to show the relationship of the model and the manufacturer.
## a. What does ggplot(mpg, aes(model, manufacturer)) + geom_point() show?
```{r}
library(ggplot2)
 ggplot(mpg, aes(model, manufacturer)) + geom_point()
```
## b. For you, is it useful? If not, how could you modify the data to make it more informative?
`It is not useful for me. It neede labels and add some colors`
```{r}
library(ggplot2)
ggplot(mpg,aes(x=model,y=manufacturer,color=model))+
  geom_point()+
  labs(title = "Model and Manufacturer",
       x="Model",
       y="Manufacturer")


```

## 3. Plot the model and the year using ggplot(). Use only the top 20 observations. Write the codes and its results.
```{r}
library(ggplot2)
mpg20<- mpg[1:20, ]

ggplot(mpg20, aes(x = model, y = year,color= model)) + geom_point() 
```

##4. Using the pipe (%>%), group the model and get the number of cars per model. Show codes and its result.
```{r}
library(dplyr)
num4<- mpg %>%
  group_by(model) %>%
  summarise(count=n())
num4
  
  
```

##a. Plot using geom_bar() using the top 20 observations only. The graphs shoudl have a title, labels and colors. Show code and results.
```{r}
library(ggplot2)
num4a<-num4[1:20,]
ggplot(num4a,aes(x=model,y=count,fill=model))+
  geom_bar(stat="Identity")+
  labs(title = "20 Observations",
       x="Model",
       y="Count")

```

##b. Plot using the geom_bar() + coord_flip() just like what is shown below. Show codes and its result
```{r}
library(ggplot2)
ggplot(num4a,aes(x=model,y=count,fill=model))+
  geom_bar(stat="Identity")+
  coord_flip()+
  labs(title = "20 Observations",
       x="Model",
       y="Count")
```

## 5. Plot the relationship between cyl - number of cylinders and displ - engine displacement using geom_point with aesthetic color = engine displacement. Title should be “Relationship between No. of Cylinders and Engine Displacement”.
## a. How would you describe its relationship? Show the codes and its result.
```{r}
library(ggplot2)
ggplot(mpg,aes(x=cyl,y=displ,color=displ))+
  geom_point()+
  labs(title = "Relationship between No. of Cylinders and Engine Displacement",
       x="No. of Cylinder",
       y="Engine Displacement")

```
##6. Plot the relationship between displ (engine displacement) and hwy(highway miles per gallon). Mapped it with a continuous variable you have identified in #1-c. What is its result? Why it produced such output?
```{r}
library(ggplot2)
ggplot(mpg,aes(x=displ,y=hwy,color=hwy))+
  geom_point()+
  labs(title = "Relationship between Engine Displacement and Highway miles per gallon",
       x="Engine Displacement",
       y="Highway miles per gallon")
```

##6. Import the traffic.csv onto your R environment.
```{r}

```
##a. How many numbers of observation does it have? What are the variables of the traffic dataset the Show your answer.
```{r}

```
##b. subset the traffic dataset into junctions. What is the R codes and its output?
```{r}

```
##c. Plot each junction in a using geom_line(). Show your solution and output.
```{r}

```

##7. From alexa_file.xlsx, import it to your environment
```{r}
library(readxl)
alexa_file <- read_excel("alexa_file.xlsx")
alexa_file
```
##a. How many observations does alexa_file has? What about the number of columns? Show your solution and answer.
```{r}
alexa<- nrow(alexa_file)
alexa
alexa7<- ncol(alexa_file)
alexa7
```
##b. group the variations and get the total of each variations. Use dplyr package. Show solution and answer.
```{r}
library(dplyr)

alexa7b<- alexa_file %>%
  group_by(variation) %>%
  summarise(count=n())

alexa7b
```
##c. Plot the variations using the ggplot() function. What did you observe? Complete the details of the graph. Show solution and answer.
```{r}
library(ggplot2)
ggplot(alexa7b,aes(x=count,y=variation,fill=variation))+
  geom_bar(stat="Identity")+
  labs(title = "Variations of the alexa_file",
       x="Count",
       y="Variations")
```

##d. Plot a geom_line() with the date and the number of verified reviews. Complete the details of the graphs. Show your answer and solution.
```{r}
library(dplyr)
alexa7d<- alexa_file %>%
  group_by(verified_reviews) %>%
  summarise(count=n())
alexa7d

alexa7d2<-alexa_file%>%
  group_by(date)
alexa7d2

alexafl<- c(alexa7d, alexa7d2)
```
```{r}
alex<-fortify(alexa_file)
alex
```

```{r}

```
##e. Get the relationship of variations and ratings. Which variations got the most highest in rating? Plot a graph to show its relationship. Show your solution and answer.
```{r}

```