---
title: "RMarkDown_Lego3b"
output:
  pdf_document: default
  html_document: default
date: "2023-10-04"
---
## R Markdown
##1. Create a data frame using the table.
##a. Write the codes.
```{r}
respo<- c(1:20)
male<- 1
female<- 2
sex<- c(female, female, male, female, female, female, female, female, female, female, male, female, female, female, female, female, female, female, male, female)
farmer<-1
driver<-2
others<-3
occupation<- c (farmer, others, others, others, farmer, driver, others, farmer, farmer, farmer, others, driver, farmer, others, others, farmer, others, farmer, driver, farmer)
person<-c(5,7,3,8,5,9,6,7,8,4,7,5,4,7,8,8,3,11,7,6)
  sibling<-c(6,4,4,1,2,1,5,3,1,2,3,2,5,5,2,1,2,5,3,2)
  wood<-1
  semi_concrete<-2
  concrete<-3
  house<- c(wood,semi_concrete,concrete,wood,wood,concrete,concrete,wood,semi_concrete,concrete,semi_concrete,concrete,semi_concrete,semi_concrete,concrete,concrete,concrete,concrete,concrete,semi_concrete)
```

```{r}
num1<-data.frame(
  respondents<- c(respo),
  sex<- c(sex),
  occupations<- c(occupation),
  person<- c(person),
  siblings<- c(sibling),
  type<-(house)
)
colnames(num1)<- c("Respondents", "Sex", "Father Occupation", "Person at Home", "Sibling at School", "Types of house")
num1
```
##b. Describe the data. Get the structure or the summary of the data.

##c. Is the mean number of siblings attending is 5?
No!!!
```{r}
mean(siblings)
```
##d. Extract the 1st two rows and then all the columns using the subsetting functions.
##Write the codes and its output.
```{r}
num1[1:2, ]
```
##e. Extract 3rd and 5th row with 2nd and 4th column. Write the codes and its result.
```{r}
num1[c(3, 5), c(2, 4)]
```

##f. Select the variable types of houses then store the vector that results as types_houses.
##Write the codes.
```{r}
types_houses<- c(house)
types_houses
```
##g. Select only all Males respondent that their father occupation was farmer. Write the codes and its output.
```{r}
num1_g<- subset(num1, sex == 1 & occupation == 1)
num1_g
```
##h. Select only all females respondent that have greater than or equal to 5 number of siblings attending school. Write the codes and its outputs.
```{r}
num1_h<- subset(num1, sex == 2 & sibling >= 5)
num1_h
```
##2. Write a R program to create an empty data frame. Using the following codes:
##df = data.frame(Ints=integer(),

##Doubles=double(), Characters=character(),
##Logicals=logical(),
##Factors=factor(),
##stringsAsFactors=FALSE)

##print("Structure of the empty dataframe:")
##print(str(df))
##a. Describe the results.

```{r}
df = data.frame(Ints=integer(),

Doubles=double(), Characters=character(),
Logicals=logical(),
Factors=factor(),
stringsAsFactors=FALSE)

print("Structure of the empty dataframe:")
print(str(df))
```
##3. Create a .csv file of this. Save it as HouseholdData.csv
#a. Import the csv file into the R environment. Write the codes.
```{r}
library(readr)
HouseholdData <- read_csv("HouseholdData.csv")
HouseholdData
```

##b. Convert the Sex into factor using factor() function and change it into integer.[Legend:Male = 1 and Female = 2].
#Write the R codes and its output.
```{r}
HouseholdData$Sex<- factor(HouseholdData$Sex, levels = c("Male" ,"Female"), labels=c(1,2))
HouseholdData
```
##c. Convert the Type of Houses into factor and change it into integer. [Legend: Wood= 1; Congrete = 2; Semi-Congrete = 3].
##Write the R codes and its output.
```{r}
HouseholdData$`Types of Houses` <- factor(HouseholdData$`Types of Houses`, levels = c("Wood" ,"Semi-congrete", "Congrete"), labels=c(1,2,3))
HouseholdData
```
##d. On father’s occupation, factor it as Farmer = 1; Driver = 2; and Others = 3.
#What is the R code and its output?
```{r}
HouseholdData$`Fathers Occupation` <- factor(HouseholdData$`Fathers Occupation`, levels = c(1,2,3), labels=c("Farmer" ,"Driver", "Others"))
HouseholdData
```
##e. Select only all females respondent that has a father whose occupation is driver.
##Write the codes and its output.
```{r}
num3_e<- subset(HouseholdData, Sex == "Female" & `Fathers Occupation` == "Farmer")
num3_e
```
##f. Select the respondents that have greater than or equal to 5 number of siblings attending school.
##Write the codes and its output.
```{r} 
num3_f<- subset(HouseholdData, `Siblings at School` >= 5)
num3_f
```
##4. Interpret the graph.
##Sentiments of Tweets Per Day
##1.July 14, 2020: There were a total of 5,800 tweets. Among these, 2,500 were negative, 1,500 were neutral, and 1,800 were positive.

##2.July 15, 2020: On this day, there were a total of 10,100 tweets. Out of these, 4,200 were negative, 2,800 were neutral, and 3,100 were positive.

##3. July 17, 2020: There were 8,100 tweets in total. Of these, 3,300 were negative, 2,000 were neutral, and 2,800 were positive.

##4.July 18, 2020: On this day, there were 8,100 tweets as well. Out of these, 3,300 were negative, 2,200 were neutral, and 2,600 were positive.

##5.July 20, 2020: There were 5,100 tweets in total. Among these, 2,300 were negative, 1,300 were neutral, and 1,500 were positive.

##6.July 21, 2020: The total number of tweets was 10,300. Out of these, 4,000 were negative, 2,800 were neutral, and 3,500 were positive.

##According to the graph the negative sentiments are most tweets per day, while positive sentiments are in second place and neutral sentiments are always been last.


