---
title: "RMarkDown_Lego#3"
output: html_document
date: "2023-10-04"
---
##USING VECTORS

##1. There is a built-in vector LETTERS contains the uppercase letters of the alphabet and letters which contains the lowercase letters of the alphabet.

```{r}
LETTERS

letters
```
##a.You need to produce a vector that contains the first 11 letters.
```{r}
num1<- LETTERS[c(1:11)]
num1
```
##b. Produce a vector that contains the odd numbered letters.
```{r}
LETTERS
odd<-LETTERS[seq( 1, 25, by=2 )]
odd
```
##c. Produce a vector that contains the vowels
```{r}
LETTERS
vowels<-LETTERS[c( 1, 5, 9, 15, 21)]
vowels
```
##Based on the above vector letters:
##d. Produce a vector that contains the last 5 lowercase letters.
```{r}
num1_d<- letters[c(22,23,24,25,26)]
num1_d
```
##e. Produce a vector that contains letters between 15 to 24 letters in lowercase.
```{r}
num1_e<- letters[seq(15, 24, by=1)]
num1_e
```

##2. Create a vector(not a dataframe) with the average temperatures in April for Tugue-garao City, Manila, Iloilo City, Tacloban, Samal Island, and Davao City. The average temperatures in Celcius are 42, 39, 34, 34, 30, and 27 degrees.
#a. What is the R code and its result for creating a character vector for the city/town of Tuguegarao City, Manila, Iloilo City, Tacloban,Samal Island, and Davao City? Name the object as city. The names should follow the same order as in the instruction.
```{r}
city<- c("Tuguegarao City", "Manila", "Iloilo City", "Tacloban", "Samal Island", "Davao City")
city
```
##b. The average temperatures in Celcius are 42, 39, 34, 34, 30, and 27 degrees.
##Name the object as temp. Write the R code and its output. Numbers should also follow what is in the instruction.
```{r}
temp<- c( 42, 39, 34, 34, 30, 27)
temp
```
##c. Create a dataframe to combine the city and the temp by using ‘data.frame(). What is the R code and its result?
```{r}
num2_c<-data.frame(
  city = c(city),
  temp = c( temp)
)
num2_c
```
  
##d. Associate the dataframe you have created in 2.(c) by naming the columns usingthe names() function. Change the column names by using names() function as City and Temperature. What is the R code and its result?
```{r}
colnames(num2_c)<-c("City", "Temperature")
num2_c
```
##e. Print the structure by using str() function. Describe the output.
```{r}
str(num2_c)
```

##f. From the answer in d, what is the content of row 3 and row 4 What is its R code and its output?
```{r}
num2_c[3:4,]
```

##g. From the answer in d, display the city with highest temperature and the city with the lowest temperature.
#What is its R code and its output?
```{r}
max(city)
min(temp)
```
##USING MATRICES
##2.Create a matrix of one to eight and eleven to fourteen with four columns and three rows.
##a. What will be the R code for the #2 question and its result?
```{r}
matrix(c(1:8, 11:14),ncol=4, nrow = 3)
```
##b. Multiply the matrix by two. What is its R code and its result?
```{r}
matrix(c(1:8, 11:14),ncol=4, nrow = 3) * 2
```
##c. What is the content of row 2? What is its R code?
```{r}
matrix(c(1:8, 11:14),ncol=4, nrow = 3) [nrow=2]
```

##d. What will be the R code if you want to display the column 3 and column 4 in row 1 and row 2?
##What is its output?
```{r}
matrix(c(1:8, 11:14),ncol=4, nrow = 3) [1:2, 3:4]
```

##e. What is the R code is you want to display only the columns in 2 and 3, row 3?
##What is its output?
```{r}
matrix(c(1:8, 11:14),ncol=4, nrow = 3) [3, 2:3]

```
##f. What is the R code is you want to display only the columns 4? What is its output?
```{r}
matrix(c(1:8, 11:14),ncol=4, nrow = 3) [1:3, 4]

```
##g. Name the rows as isa, dalawa, tatlo and columns as uno, dos, tres, quatro for the matrix that was created in b.‘.
##What is its R code and corresponding output?
```{r}
matrix<-matrix(c(1:8, 11:14),ncol=4, nrow = 3)
rownames(matrix)<-c( "isa", "dalawa", "tatlo")
colnames(matrix)<- c("uno", "dos", "tres", "quatro")
matrix

```

##h. From the original matrix you have created in a, reshape the matrix by assigning anew dimension with dim(). New dimensions should have 2 columns and 6 rows. 
##What will be the R code and its output?
```{r}
dim(matrix)<- c(2,6)
```

##USING ARRAYS

##An array contains 1, 2, 3, 6, 7, 8, 9, 0, 3, 4, 5, 1

##a. Create an array for the above numeric values. Each values will be repeated twice
##What will be the R code if you are to create a three-dimensional array with 4 columns and2 rows. What will be its output?
```{r}
array_dta <- array(c(1, 2, 3, 6, 7, 8, 9, 0, 3, 4, 5, 1)*2)
dim_array<- array(array_dta, dim= c(2 ,4 ,3))
dim_array
```
##b. How many dimensions do your array have?
```{r}
dim(dim_array)
```

##c. Name the rows as lowercase letters and columns as uppercase letters starting fromthe A. The array names should be “1st-Dimensional Array”, “2nd-Dimensional Array”, and“3rd-Dimensional Array”.
##What will be the R codes and its output?

```{r}
dimnames(dim_array)<- list(
  c("a","b"),
  c("A", "B", "C", "D"),
  c("1st-Dimensional Array", "2nd-Dimensional Array", "3rd-Dimensional Array" )
)
dim_array
```